---
title: "Homework-2"
output: html_notebook
---
Function in R
A function is defined by an assignment of the form

name <- function() expression
for example

```{r}
sum <- function(){
  1+1
}

value <- sum()
value
```
You can add arguments in function
```{r}
squared_value <- function(n){
  n^2
}

value <- squared_value(10)
value
```

The '...' argument
Another frequent requirement is to allow one function to pass on argument settings to another. 


```{r}

sumar_numero_impares <- function(...)
{
  
  values <- c(...)
  if(!is.numeric(values)) return('NaN')
 
  cont <- 0
  for(n in values){
    if(n%%2 != 0){
      cont <- cont + n
    }
  }
cont
}

sumar_numero_impares(c(1,2,3,4,5,6,8,2,4,2,35,5))

```
  
Default values

```{r}
whileFunc <- function(x, limit=10){
  cont <- 0
  while(cont <= limit){
      print(cont)  
    cont <- cont + 1
  }
}
whileFunc(15)
```
Family Apply: lapply, sapply, vapply

lapply: applies a function to a list or a vector, returning a list of the same length as the input.
for example, we use square_value fuction declared above

```{r}
vecLapply <-  c(12, 18, 6,9,64)
lapply(vecLapply, squared_value)
```

sapply: The main difference between the functions is that lapply returns a list instead of an array. However,
if you set simplify = FALSE to the sapply function both will return a list.

for example
```{r}
vecSapply <-  c(12, 18, 6,9,64)
sapply(vecLapply, squared_value)
sapply(vecLapply, squared_value, simplify = FALSE)
```

vapply: is similar that the sapply function, but when using vapply we need to specify the output type explicitly. 
In this example, we will return an numeric

```{r}
vecVapply <-  c(12, 18, 6,9,64)
vapply(vecVapply, squared_value, FUN.VALUE = numeric(1))
```



